Pool Model - A unified Mathematical\\ Modeling Framework for Food Science

### 2025-11-06 paper/pool_model.tex
Add units to captions for pool model

$N_t$ denotes the maximal size of the total bacterial population due to environmental limitations (Figure \ref{fig:3pool_resource_plots}).

@@

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\alpha=2.5$, $\mu'=0.5$.
        The blue curve shows a significant dip in the behavior of the system where the death of the bacteria is present $\mu = 0.5$.
        Other curves show the case of no bacteria dying $\mu=0$ and represent different lengths of lag phases: short $\lambda=10^{-2}$ (dark green), intermediate $\lambda=10^{-3}$ (light green) and long one $\lambda=10^{-4}$ (yellow). Note that the steady state for $N(t)$ and $D(t)$ is for this model $\lim_{t\to\infty} N(t)=0$ and $\lim_{t\to\infty} D(t)=N_t$, because of the depletion of the resource pool. 

@@

        The curves represent no temperature shift (green), one temperature jump $\Delta T = 10$ at time $t=4$ (orange)
        and the series of different temperature shifts of value 10, 5 and 15 at the time points 1, 3 and 7, respectively (rose).
        The parameters of the back-flow rate are $\Gamma=1$ and $\delta=5$.
        The other model parameters are $\alpha=2.5$, $\mu'=0.5$, $\beta=5$, $\lambda=10^{-2}$, $\mu = 0$ for each curve.

@@

        The competition of the two bacterial species due to the common limiting resource calculated using equation~(\ref{eq:model_2sp_resource_comp}).
        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}$, $\alpha_A=3.0$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}$, $\alpha_B=2.5$.

@@

        Spatial configuration of cells corresponding to the pictures shown in figure~\ref{fig:spatial-growth-curve}.

>>>>

$N_t$ denotes the maximal size of the total bacterial population due to environmental limitations.

@@

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\alpha=2.5~\mathrm{s}^{-1}$, $\mu'=0.5~\mathrm{s}^{-1}$, $N_t = 10^4$.
        The blue curve shows a significant dip in the behavior of the system where the death of the bacteria is present $\mu = 0.5~\mathrm{s}^{-1}$.
        Other curves show the case of no bacteria dying $\mu=0~\mathrm{s}^{-1}$ and represent different lengths of lag phases: short $\lambda=10^{-2}~\mathrm{s}^{-1}$ (dark green), intermediate $\lambda=10^{-3}~\mathrm{s}^{-1}$ (light green) and long one $\lambda=10^{-4}~\mathrm{s}^{-1}$ (yellow). Note that the steady state for $N(t)$ and $D(t)$ is for this model $\lim_{t\to\infty} N(t)=0$ and $\lim_{t\to\infty} D(t)=N_t$, because of the depletion of the resource pool.

@@

        The curves represent no temperature shift (green), one temperature jump $\Delta T = 10^\circ C$ at time $t=4~\mathrm{s}$ (orange)
        and the series of different temperature shifts of value $10^\circ C$, $5^\circ C$ and $15^\circ C$ at the time points $1, 3$ and $7$, respectively (rose).
        The parameters of the back-flow rate are $\Gamma=1^\circ C / s$ and $\delta=5~\mathrm{s}^{-1}$.
        The other model parameters are $\alpha=2.5~\mathrm{s}^{-1}$, $\mu'=0.5~\mathrm{s}^{-1}$, $\beta=5~\mathrm{s}^{-1}$, $\lambda=10^{-2}~\mathrm{s}^{-1}$, $\mu = 0~\mathrm{s}^{-1}$ for each curve.

@@

        The competition of the two bacterial species due to the common limiting resource calculated using equations~(\ref{eq:model_2sp_resource_comp}).

@@

        Spatial configuration of cells corresponding to the pictures shown in Figure~\ref{fig:spatial-growth-curve}.
